\documentclass[11pt, a4paper, roman]{moderncv}

\moderncvtheme[blue]{banking}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.9]{geometry}
\usepackage{multicol}

\name{Zach}{Sahlin}
\email{zach@sahlins.net}
\mobile{206-607-7655}
\social[github]{GoneSahlin}

\newcommand{\project}[5]{
	\textbf{#1}
%	\href{#2}{\:\small\faGithub\:}
	$|$ #3 
	\hfill\textit{#4}
	#5
	\vspace{2mm}
}

\newcommand{\entry}[4]{
	\textbf{#1}\:$|$\:#2 
	\hfill\textit{#3}
	#4
	\vspace{2mm}
}

\newcommand{\education}[5]{
	\textbf{#1} $|$ #2
	\hfill#3
	\\\textit{#4}
	#5
	\vspace{2mm}
}

\begin{document}
\maketitle
\vspace*{-12mm}

\begin{multicols}{2}

\section{RELATED COURSEWORK}
{\begin{itemize}
    \item Algorithms \& Abstract Data Structures
    \item Machine Learning \& Intelligent Systems
    \item Operating Systems
    \item Database Management Systems
    % \item Software Development
    \item Data Science Algorithms
    \item Programming Languages \& Compilers
  \end{itemize}
} 

\columnbreak  


\section{TECHNICAL SKILLS}
{\begin{itemize}
    \item Languages: C++, Java, Python
    \item Tools: Git, Linux, Docker, Jupyter, Postgres
    \item Libraries: pandas, NumPy, scikit-learn, Matplotlib
  \end{itemize}
}
\end{multicols}
\vspace*{-2mm}
\section{EDUCATION}

\education{Gonzaga University}{Spokane, WA}{August 2019 -- Expected May 2023}{BS in Computer Science, Minor in Applied Mathematics}
	{\begin{itemize}
    		\item GPA: 3.8
    		\item President's List: Fall 2019, Spring 2020, Spring 2021
    		\item Dean's List: Fall 2020, Fall 2021, Spring 2022
  	\end{itemize}
}

\vspace*{-2mm}
\section{PROJECTS}

{\project{Machine Learning for Real Estate}{}{Python, SQL, JS}{Ongoing}
	{\begin{itemize}
		\item Senior Design Project
		\item Collects data on historical rental prices.
		\item Predicts future rental prices.
		\item Displays historical prices and predictions as a web app.
	\end{itemize}}
}

{\project{Stock Analyzer}{}{Python, Postgres, selenium}{Summer 2022}
	{\begin{itemize}
		\item Collects historical and current data from various sources using APIs and webscraping.
		\item Performs analysis on current market trends.
		\item Provides user with information on when to buy, hold, or sell stocks.
	\end{itemize}}
}

{\project{Fantasy Football Drafter}{https://github.com/GoneSahlin/fantasydraft}{Python, Sphinx}{Fall 2021}
	{\begin{itemize}
		\item Models a fantasy football draft to use for testing.
		\item Tests and compares different drafting algorithms against each other.
		\item Uses Sphinx to create documentation.
	\end{itemize}}
}
{\project{Spotify Predictor}{https://github.com/GoneSahlin/CPSC222Final}{Python, pandas, scikit-learn, Matplotlib}{Fall 2020}
	{\begin{itemize}
    		\item Uses a decision tree and kNN to predict whether I will skip a song with an 81\% accuracy.
    		\item Connects to the Spotify API to gather additional data on each song.
   		 \item Uses Matplotlib to create plots to analyze the dataset.
	\end{itemize}}
}
%{\project{Nim Solver}{https://github.com/GoneSahlin/Nim}{Python}{Fall 2021}
%	{\begin{itemize}
%    		\item Models and plays the game of Nim using the optimal strategy for both 2 and 3 player games.
%    		\item Builds a graph of all possible states, calculates each state's probability of winning, and picks the best move.
%	\end{itemize}}
%}
{\project{Ski Resort Database}{https://github.com/GoneSahlin/321_Final_Project}{SQL, HTML, PHP}{Fall 2021}
	{\begin{itemize}
    		\item Connects webpages to a mySQL database to display information on ski resorts.
	\end{itemize}}
}
%{\project{Yahtzee}{https://github.com/Gonzaga-University/yahtzee-final-game-a-a-r-o-n}{Java, Swing, JUnit}{Spring 2021}
%	{\begin{itemize}
%    		\item Models Yahtzee with a resizable GUI and customizable settings and utilizes JUnit to implement unit testing.
%	\end{itemize}}
%}
%{\project{Bike Trail Classifier}{https://github.com/GoneSahlin/BikeTrailSVM}{Python, pandas, scikit-learn}{Fall 2021}
%	{\begin{itemize}
%    		\item Classifies bike trails into difficulties using a SVM with a 66\% accuracy.
%	\end{itemize}}
%}
%{\project{Linux Kernel Module}{https://github.com/GU-2021-Fall-CPSC346/hw5-linux-kernel-module-dev-GoneSahlin}{C}{Fall 2021}
%	{\begin{itemize}
%   		\item Modifies the Linux kernel with a simple module that can be loaded and unloaded.
%	\end{itemize}}
%}

\vspace*{-2mm}
\section{WORK EXPERIENCE}

\entry{Gonzaga University}{Teaching Assistant}{August 2022 -- Present}
{\begin{itemize}
	\item Teaching assistant for 2 sections of Operating Systems.
	\item Grading programming and written assignments.
\end{itemize}
}

\entry{iD Tech}{Online Private Instructor}{June 2021 -- August 2022}
{\begin{itemize}
    \item Tutored in 8 different computer science topics, including C++, Java, and Python.
    \item Completed over 200 private lessons.
    % \item Completed over 100 private lessons in various computer science topics including C++, Java, and Python.
    \item Built relationships with long-term clients, and developed further skills in communication and coding.
    \item Collaborated with other instructors to improve teaching methods.
  \end{itemize}
}

%{\entry{University Presbyterian Church}{Kitchen and Event Assistant}{August 2018 -- August 2019}
%	{\begin{itemize}
%   		\item Worked in a team to prepare food for congregants and homeless, numbering up to 700 people.
%    		\item Led groups of volunteers to serve food for the international community.
%  	\end{itemize}}
%}

%\vspace*{-2mm}
% \section{VOLUNTEER EXPERIENCE}
%{\entry{Camp Side-By-Side}{Volunteer}{July 2019}
%	{\begin{itemize}
%		\item Volunteered at a week-long camp for families of Seattle Children's patients with a serious illness.
%     		\item Served as a "buddy" for sibling of a seriously ill patient, accompanying him in all camp activities.
%	\end{itemize}}
%}

\end{document}